Multi-reference pangenome graphs

### 2022-01-12 manuscript/main.tex

\begin{proof}
By definition \ref{def:vg}, two paths have identical subsequences where they walk (or ``step'') through the same series of oriented nodes (e.g. $s_1 s_2 s_3$).
An identical set of path steps is thus equivalent to a sequence match.
Pairwise alignments are by definition collections of matches between sequences.
The variation graph thus models a set of pairwise alignments between paths in $P$.
\end{proof}

@@

\begin{proof}
After the first step of induction, the graph represents all pairwise matches in $m_1^+$.
Each subsequent step includes progressively more of $A$, until at completion, all pairwise relationships are accounted for in $V$.
The paths of the variation graph are equivalent to input sequences, and the path relationship within the graph is defined by their alignments.
\end{proof}

>>>>

\begin{proof}
By definition \ref{def:vg}, two paths have identical subsequences where they walk (or ``step'') through the same series of oriented nodes (e.g. $s_1 s_2 s_3$).
An identical set of path steps is thus equivalent to a sequence match.
Pairwise alignments are by definition collections of character-level matches between sequences.
The variation graph thus models a set of pairwise alignments between paths in $P$.
\end{proof}

@@

\begin{proof}
After the first step of induction, the graph represents all pairwise matches in $m_1^+$.
Each subsequent step includes progressively more of $A$, until at completion, all pairwise relationships are accounted for in $V$.
%All characters in $S$ have been accounted for in $V$, and we can make this mapping explicit by tracing $S$ through the
%The paths of the variation graph are equivalent to input sequences, and the path relationship within the graph is defined by their alignments.
\end{proof}
